---
title: "TidyTues6"
author: "Hanalei"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE)
```

# So I did a dumb and accidentally skipped ahead last week for Tidy Tuesday. This week I will be going back to work on the dataset I missed last week.

```{r}
library(tidyverse)
library(ggplot2)
library(here)
```


```{r}
cbp_resp <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-11-26/cbp_resp.csv')
cbp_state <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-11-26/cbp_state.csv')
```
## This dataset is enormous... so enormous that my laptop could not handle running most tasks without the app crashing or task failing. Because of that, I had to do something a little boring with the data

```{r}
agg_data_year_demographic <- cbp_state %>%
  group_by(fiscal_year, demographic) %>%
  summarise(total_encounter_count = sum(encounter_count), .groups = 'drop')

```

### Still, I learned what an area plot is and how to incorporate it. I intended to make a PCA but my laptop seriously almost caught fire so I didnʻt end up doing that.

```{r}
ggplot(agg_data_year_demographic, aes(x = fiscal_year, y = total_encounter_count, fill = demographic)) +
  geom_area() +
  labs(title = "Stacked Area Plot of Encounters by Demographic",
       x = "Fiscal Year", y = "Total Encounters") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3")

ggsave(here("TidyTues","TTweek_06", "output", "AreaPlotTT6.png"))
```

